\documentclass[11pt]{article}

\usepackage{fancyhdr}
\usepackage{style}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[yyyymmdd]{datetime}
\usepackage[letterpaper, margin=0.5in, top=0.8in]{geometry}

\newdateformat{mydate}{\shortmonthname[\THEMONTH] \THEYEAR}
\mydate

\newcommand{\daterange}[4]{\formatdate{1}{#1}{#2} - \formatdate{1}{#3}{#4}}
\newcommand{\daterangepres}[2]{\formatdate{1}{#1}{#2} - Present}
\newcommand{\tetrio}{\textsc{tetr.io}\ }

\setlength\parindent{0pt}

\pagenumbering{gobble}
\pagestyle{fancy}

\begin{document}

\fancyhead[R]{Github \\ LinkedIn}
\fancyhead[C]{\Huge \textbf{Ian Chen}}

\fancyhead[L]{ianchen3@illinois.edu \\ (650) 505-6879}

\section*{Education}
\vspace*{-2mm}

\textbf{University of Illinois} Urbana-Champaign, College of Liberal Arts and Sciences \hfill \daterangepres{8}{2024} \\
\emph{Major in Statistics \& Computer Science} --- \emph{Cumulative GPA}: 3.98 / 4.00 \\
\textbf{Henry M. Gunn High School} Palo Alto, California \hfill \daterange{8}{2019}{5}{2023} \\
\emph{Cumulative GPA}: 4.33 / 4.00 \\

\vspace*{-5mm}
\rule{\textwidth}{0.1pt}
\vspace*{-10mm}

\section*{Technical Skills}
\vspace*{-2mm}

\textbf{Programming Languages; Tools} \\
Python, C++, C\#, Rust, Bash, \textsc{sql}; Git, \LaTeX \\

\vspace*{-5mm}
\rule{\textwidth}{0.1pt}
\vspace*{-10mm}

\section*{Work Experience}
\vspace*{-2mm}

\textbf{University of Illinois} \\
\emph{Computer Architecture Course Assistant} \hfill \daterangepres{8}{2024} {
\begin{itemize}
	\cramped
	\item TBD
\end{itemize}
\emph{Physics Mechanics Learning Assistant} \hfill \daterange{1}{2024}{5}{2024}
\begin{itemize}
	\cramped
	\item Designed laboratory experiments modeling real world scenarios according to ISLE guidelines.
	\item Mentored introductory physics lab classes at scale (75+ students)
\end{itemize}

\textbf{Maven Optronics} \hfill \daterange{5}{2024}{8}{2024} \\
\emph{Software Engineer Intern}
\begin{itemize}
	\cramped
	\item Implemented Manufacturing Execution System (MES) materials traceability modules — populated mySQL tables to link raw material barcode IDs (with photo records) to assembled MiniLED boards.
	\item Developed automatic deployment of software releases via win32 installer (.msi) through administrative installation across NAS server.
	\item Developed Windows Desktop applications to automatically create Certificate of Analysis reports with syndicated IPQC \& FQC inspection data.
\end{itemize}

\rule{\textwidth}{0.1pt}
\vspace*{-10mm}

\section*{Projects}
\vspace*{-2mm}

\textbf{Directle: NLP-enabled linguistics game} \hfill \daterange{1}{2024}{5}{2024}
\begin{itemize}
	\cramped
	\item Collaborated with three team members to build a full-stack website hosting an English word game. The game guides players to guess a secret word through one-word semantic clues.
	\item Implemented a word2vec NLP model using the top 10M wikipedia articles which projected vocabulary into low-dimensional embeddings, allowing for quantification of word similarities.
	\item Developed and deployed a backend REST API to query word vectors stored in a Postgres database and integrated with frontend React server.
\end{itemize}

\textbf{IVFish: Tetris AI $\gg$ Human} (\url{https://github.com/ivfish/bot}) \hfill \daterange{6}{2021}{8}{2023}
\begin{itemize}
	\cramped
	\item Collaborated with two team members to develop an AI bot to compete in multiplayer Tetris on \tetrio server with over 4 million players. This bot successfully defeated a top 10 ranked player in the server
	\item Implemented massive graph (30M+ nodes) parallel searching algorithms with specialized heuristics to search for optimal next moves within milliseconds.
	\item Achieved 10x performance improvement in the graph search algorithm by optimizing code at the microarchitecture level through Intel hardware intrinsics.
	\item Established websocket network protocol for communication with \tetrio multiplayer Tetris server.
\end{itemize}

\rule{\textwidth}{0.1pt}
\vspace*{-10mm}

\section*{Relevant Coursework}
\vspace*{-2mm}

\textbf{Computer Science}
\emph{Computer Architecture};
\emph{Systems Programming};
\emph{Data Structures};
\emph{Algorithms}

\textbf{Statistics \& Math}
\emph{Probability I \& II};
\emph{Linear Algebra};
\emph{Differential Equations};

\textbf{Physics}
\emph{Mechanics};
\emph{E\&M};
\emph{Thermodynamics};
\emph{Quantum Physics}

\end{document}
